Supermassive black holes and their host spheroids \\ III. Mbh-n paper

### 2015-11-06 papers/mbhn/mbhn.tex
friday

\shorttitle{Mbh-n paper}
\shortauthors{Savorgnan et al.}

@@

\title{Mbh-n paper}

@@

\section{Data}
We populated the $L_{\rm sph} - n_{\rm sph}$ and $M_{\rm BH} - n_{\rm sph}$ diagrams 
with the same galaxy sample (Table \ref{tab:sample}) used in \emph{Paper II}, 
i.e.~66 galaxies for which a dynamical measurement of the black hole mass has been reported in the literature 
(by \citealt{grahamscott2013} or \citealt{rusli2013}) 
and for which we were able to successfully model the light distribution and measure the spheroid structural parameters 
using $3.6\rm~\mu m$ \emph{Spitzer} satellite images. 
Our galaxy decompositions take into account bulge, disks, spiral arms, bars, rings, halo, 
extended or unresolved nuclear source and partially depleted core, 
and -- for the first time -- they were checked to be consistent with the galaxy kinematics 
\citep{atlas3dIII,scott2014,arnold2014}. 
Kinematical information was used to confirm the presence of disk components 
in the majority of early-type (elliptical + lenticular) galaxies and, more importantly,  
to estabilish the radial extent of these disks, 
which in most cases is not obvious from a visual inspection of the galaxy images. 
This enabled us to distinguish between intermediate-scale disks, 
that are fully embedded in the spheroid,  
and large-scale disks, that encase the bulge and dominate the light at large radii.  
Savorgnan \& Graham (2015) explain that when an intermediate-scale disk is misclassified and modeled as a large-scale disk, 
the luminosity of the spheroid is underestimated, 
hence the galaxy incorrectly appears as a positive outlier (an ``over-massive'' black hole) in the $M_{\rm BH} - L_{\rm sph}$ diagram. 
A detailed description of the dataset used here, the data reduction process and the galaxy modelling technique that we developed 
can be found in \emph{Paper I}, 
along with a discussion of how we estimated the uncertainties on the spheroid S\'ersic indices\footnote{The uncertainties associated with 
the spheroid S\'ersic indices have been estimated with a method that takes into account systematic errors. 
This method consists in comparing, for each of our galaxies, the measurements of the spheroid S\'ersic index obtained by different studies 
with that obtained by us. 
Systematic errors are typically not considered by popular 2D fitting codes which report only the statistical errors 
associated with their fitted parameters. 
Refer to \emph{Paper I} for a detailed discussion on this. }.  
The morphological classification (E = elliptical; E/S0 = elliptical/lenticular; S0 = lenticular; 
S0/Sp = lenticular/spiral; Sp = spiral; and ``merger'') follows from the galaxy decompositions illustrated in \emph{Paper I}. 
As in \emph{Paper II}, we will refer to early-type galaxies (E+S0) and late-type galaxies (Sp). 
The early-type bin includes the two galaxies classified as E/S0, 
whereas the two galaxies classified as S0/Sp and the two galaxies classified as mergers are included in neither the early- nor the late-type bin.

@@

\section{Analysis and results}
As in \emph{Paper II}, a linear regression analysis of the $L_{\rm sph} - n_{\rm sph}$ 
(Table \ref{tab:lregLn} and Figure \ref{fig:magn})
and $M_{\rm BH} - n_{\rm sph}$ (Table \ref{tab:lregMn} and Figure \ref{fig:mbhn}) diagrams 
was performed using three different routines: 
the BCES code from \cite{akritasbershady1996}, 
the FITEXY routine \citep{press1992}, as modified by \cite{tremaine2002}, 
and the Bayesian estimator {\tt linmix\_err} \citep{linmixerr}.
All of these three routines take into account the intrinsic scatter, 
but only the FITEXY and the {\tt linmix\_err} codes allow one to quantify it.
We report both symmetrical and nonsymmetrical linear regressions.  
Symmetrical regressions are meant to be compared with theoretical expectations, 
whereas nonsymmetrical forward ($Y|X$) regressions -- which minimize the scatter in the $Y$ direction -- 
allow one to predict the value of the observable $Y$ with the best possible precision. \\
We searched for extreme outliers in both the $L_{\rm sph} - n_{\rm sph}$ and $M_{\rm BH} - n_{\rm sph}$ diagrams, 
and found that in our $L_{\rm sph} - n_{\rm sph}$ plot there are no $3\sigma$ outliers, 
whereas in our $M_{\rm BH} - n_{\rm sph}$ plot 
the S0 galaxies NGC 0524 and NGC 3998 reside more than $3\sigma$ from the bisector linear regression for all galaxies. 
These two galaxies have therefore been excluded from the rest of the analysis. \\
{\bf fitexy does better job, we report that} \\

\subsection{$L_{\rm sph} - n_{\rm sph}$}
Following \cite{graham2001}, 
who showed that the $L_{\rm sph} - n_{\rm sph}$ relation is different for elliptical galaxies and the bulges of disk galaxies (S0+Sp), 
\cite{savorgnan2013} re-analyzed the data from \cite{grahamguzman2003} and \cite{graham2013review} 
and obtained two separate $L_{\rm sph} - n_{\rm sph}$ linear regressions for elliptical galaxies and the bulges of disk galaxies 
(in the B- and K-band, respectively). 
At the time, the $L_{\rm sph} - n_{\rm sph}$ datasets from \cite{grahamguzman2003} and \cite{graham2013review} were of the best quality available 
to investigate the $L_{\rm sph} - n_{\rm sph}$ relation for different galaxy morphological types. 
However, these datasets were not obtained from a homogeneous analysis, 
but they were a collection of results taken from various past bulge/disk decomposition studies. 
It is also worth mentioning that, 
although the K-band luminosities of the bulges of disk galaxies had been corrected for internal dust absorption, 
{\bf the dust corrections are not precise today refs??, imagine at the time.....}  
Here we re-investigate the $L_{\rm sph} - n_{\rm sph}$ diagram with our high-quality dataset  
derived from state-of-the-art multicomponent galaxy decompositions, 
that were performed in a consistent manner 
and using the $3.6\rm~\mu m$ band, which is less affected by dust extinction than the K-band. \\
\cite{graham2013review} presented a single $L_{\rm sph} - n_{\rm sph}$ correlation for the bulges of disk galaxies (S0+Sp).
However, using our dataset, 
we fit the $L_{\rm sph} - n_{\rm sph}$ relation for elliptical, lenticular and spiral galaxies separately, 
and found that the values of the slope and intercept for the lenticular galaxies 
are not consistent within the errors with those for the spiral galaxies, 
but are consistent within the errors with those for the elliptical galaxies.  
Given this, we conclude that in the $L_{\rm sph} - n_{\rm sph}$ diagram 
elliptical and lenticular galaxies form together a single (\emph{early-type}) sequence, 
whereas the combination of lenticular and spiral galaxies do not. 
{\bf why?? dust? multicomponent? classification?}

\begin{figure}[h]
\begin{center}
\includegraphics[width=\columnwidth]{images/mag_vs_n_maj.pdf}
\caption{Spheroid absolute magnitude (at $3.6\rm~\mu m$) plotted against spheroid S\'ersic index 
measured along the galaxy major-axis. 
Symbols are coded according to the galaxy morphological type (see legend).
{\bf crosses outliers!} 
The red dashed line indicates the FITEXY bisector linear regression for the $45-2=43$  early-type galaxies (E+S0), 
with the red shaded area denoting its $1\sigma$ uncertainty. 
The shallower blue solid line shows the FITEXY bisector linear regression for the bulges of the 17 late-type (Sp) galaxies, 
with the blue shaded area denoting its $1\sigma$ uncertainty. 
The inset panel shows the error bars associated to each data point,  
where the error bars have the same color coding as the symbols in the main figure. 
}
\label{fig:magn}
\end{center}
\end{figure}

\subsection{$M_{\rm BH} - n_{\rm sph}$}
\cite{grahamscott2013} presented two different $M_{\rm BH} - L_{\rm sph}$ relations for S\'ersic and core-S\'ersic 
spheroids\footnote{Core-S\'ersic spheroids have partially depleted cores relative to their outer S\'ersic light profile, 
whereas S\'ersic spheroids have no central deficit of stars. } \citep{graham2003coresersicmodel,trujillo2004coresersicmodel}.
However, in \emph{Paper II} we found that the slopes of the correlations for S\'ersic and core-S\'ersic spheroids 
are consistent with each other within their $1\sigma$ uncertainties, 
which prevents us from considering them as two separate correlations. 
On the other hand, our analysis showed that early- and late-type galaxies follow two different $M_{\rm BH} - L_{\rm sph}$ relations 
($M_{\rm BH} \propto L_{\rm sph}^{1.00 \pm 0.10}$ 
and $M_{\rm BH} \propto L_{\rm sph}^{2.88 \pm 0.68}$, respectively). \\
Given that early- and late-type galaxies define two separate sequences in both the $L_{\rm sph} - n_{\rm sph}$ 
and $M_{\rm BH} - L_{\rm sph}$ diagrams, 
we investigate substructure in the $M_{\rm BH} - n_{\rm sph}$ diagram. 
Using the results from the modified FITEXY routine, 
we report that 
early-type galaxies follow $M_{\rm BH} \propto n_{\rm sph}^{3.58 \pm 0.27}$, 
while late-type galaxies follow $M_{\rm BH} \propto n_{\rm sph}^{4.55 \pm 0.66}$. 
The Bayesian estimator {\tt linmix\_err} returns consistent results: 
a slope of $3.44 \pm 0.33$ for the early-type galaxies 
and a slope of $4.12 \pm 1.07$ for the late-type galaxies. 
In both cases, the values of the slope and intercept for the early- and late-type galaxies 
are consistent with each other within their $1\sigma$ uncertainties\footnote{In effect, 
considering the results of the modified FITEXY routine, 
the slopes of the relations for early- and late-type galaxies 
are only marginally consistent with each other within their $1\sigma$ uncertainties. 
However, the slopes obtained with Bayesian estimator {\tt linmix\_err} 
are fully consistent with each other within their $1\sigma$ uncertainties. }
Our analysis shows that the early- and late-type galaxies do not define two separate trends in the $M_{\rm BH} - n_{\rm sph}$ diagram, 
i.e.~we do not identify any significant substructure based on the galaxy morphological type. 
The symmetrical linear regression for all galaxies obtained with the modified FITEXY routine is: 
\begin{equation}
\log \biggl( \frac{M_{\rm BH}}{\rm M_\odot} \biggr) = (8.18 \pm 0.06) + (3.39 \pm 0.15) \bigl(\log n_{\rm sph} - 0.51 \bigr) .
\end{equation}

\begin{figure}[h]
\begin{center}
\includegraphics[width=\columnwidth]{images/mbh_vs_n_maj.pdf}
\caption{Black hole mass plotted against spheroid S\'ersic index measured along the galaxy major-axis. 
Symbols are coded according to the galaxy morphological type (see legend). 
{\bf crosses outliers!} 
The red dashed line indicates the FITEXY bisector linear regression for the $45-2=43$  early-type galaxies (E+S0), 
with the red shaded area denoting its $1\sigma$ uncertainty. 
The shallower blue solid line shows the FITEXY bisector linear regression for the bulges of the 17 late-type (Sp) galaxies, 
with the blue shaded area denoting its $1\sigma$ uncertainty. 
The linear regressions for early- and late-type galaxies are consistent with each other within their $1\sigma$ uncertainties.  
The inset panel shows the error bars associated to each data point,  
where the error bars have the same color coding as the symbols in the main figure. 
}
\label{fig:mbhn}
\end{center}
\end{figure}

\section{Discussion and conclusions}

intr scatter of correlation for all?\\
data suggest that m-n more fundamental than l-n or m-l woooooh? \\

\begin{table*}
\centering
\caption{Linear regression analysis of the $L_{\rm sph} - n_{\rm sph}$ diagram.}
\begin{tabular}{llccccc}
\tableline
\tableline
{\bf Subsample (size)} & {\bf Regression} & $\boldsymbol \alpha$ & $\boldsymbol \beta$ & $\boldsymbol \langle \log n_{\rm sph} \rangle$ & $\boldsymbol \epsilon$ & $\boldsymbol \Delta$ \\ 
\tableline 
\\
 & \multicolumn{6}{l}{$MAG_{\rm sph}/{\rm [mag]} = \alpha + \beta \bigl(\log n_{\rm sph} - \langle \log n_{\rm sph,maj} \rangle \bigr)$} \\ [0.5em]
All (62)               & BCES $(Y|X)$               & $-23.88 \pm 0.15$ & $-7.17 \pm 0.80$ & $0.51$ & $-$ & $1.18$ \\
                       & mFITEXY $(Y|X)$            & $-23.95 \pm 0.13$ & $-6.70 \pm 0.45$ & $0.51$ & $0.56^{+0.15}_{-0.10}$ & $0.98$ \\
                       & {\tt linmix\_err} $(Y|X)$  & $-23.92 \pm 0.15$ & $-6.40 \pm 0.57$ & $0.51$ & $0.74 \pm 0.13$ & $1.07$ \\ [0.5em]
                       & BCES $(X|Y)$               & $-23.88 \pm 0.14$ & $-6.70 \pm 0.51$ & $0.51$ & $-$ & $1.11$ \\
                       & mFITEXY $(X|Y)$            & $-23.94 \pm 0.14$ & $-7.50 \pm 0.52$ & $0.51$ & $0.59^{+0.17}_{-0.11}$ & $1.23$ \\
                       & {\tt linmix\_err} $(X|Y)$  & $-23.94 \pm 0.16$ & $-7.51 \pm 0.62$ & $0.51$ & $0.81 \pm 0.16$ & $1.23$ \\ [0.5em]
                       & BCES Bisector              & $-23.88 \pm 0.14$ & $-6.93 \pm 0.60$ & $0.51$ & $-$ & $1.14$ \\
                       & mFITEXY Bisector           & $-23.94 \pm 0.13$ & $-7.08 \pm 0.34$ & $0.51$ & $-$ & $1.16$ \\
                       & {\tt linmix\_err} Bisector & $-23.93 \pm 0.16$ & $-6.91 \pm 0.42$ & $0.51$ & $-$ & $1.14$ \\ [0.5em]

@@

\begin{table*}
\centering
\caption{Linear regression analysis of the $L_{\rm sph} - n_{\rm sph}$ diagram.}
\begin{tabular}{llccccc}
\tableline
\tableline
{\bf Subsample (size)} & {\bf Regression} & $\boldsymbol \alpha$ & $\boldsymbol \beta$ & $\boldsymbol \langle \log n_{\rm sph} \rangle$ & $\boldsymbol \epsilon$ & $\boldsymbol \Delta$ \\ 
\tableline 
\\
Early-type (E+S0) (43) & BCES $(Y|X)$		    & $-24.55 \pm 0.22$ & $-11.84 \pm 2.29$ & $0.64$ & $-$ & $1.50$ \\
		       & mFITEXY $(Y|X)$	    & $-24.74 \pm 0.14$ & $-8.86 \pm 0.66$ & $0.51$ & $0.27^{+0.20}_{-0.27}$ & $0.87$ \\
		       & {\tt linmix\_err} $(Y|X)$  & $-24.70 \pm 0.17$ & $-8.28 \pm 0.87$ & $0.64$ & $0.58 \pm 0.17$ & $0.98$ \\ [0.5em]
		       & BCES $(X|Y)$		    & $-24.55 \pm 0.14$ & $-8.25 \pm 0.63$ & $0.64$ & $-$ & $0.96$ \\
		       & mFITEXY $(X|Y)$	    & $-24.74 \pm 0.14$ & $-9.13 \pm 0.68$ & $0.64$ & $0.23^{+0.25}_{-0.23}$ & $1.08$ \\
		       & {\tt linmix\_err} $(X|Y)$  & $-24.73 \pm 0.18$ & $-9.08 \pm 0.87$ & $0.64$ & $0.60 \pm 0.21$ & $1.07$ \\ [0.5em]
		       & BCES Bisector  	    & $-24.55 \pm 0.17$ & $-9.73 \pm 1.05$ & $0.64$ & $-$ & $1.14$ \\
		       & mFITEXY Bisector	    & $-24.74 \pm 0.14$ & $-8.99 \pm 0.48$ & $0.64$ & $-$ & $1.06$ \\
		       & {\tt linmix\_err} Bisector & $-24.72 \pm 0.17$ & $-8.66 \pm 0.63$ & $0.64$ & $-$ & $1.02$ \\ [0.5em]

@@

>>>>

\shorttitle{Mbh-n paper}
\shortauthors{Savorgnan \& Graham}

@@

\title{Supermassive black holes and their host spheroids \\ III. Mbh-n paper}

@@

\section{Data}
We populated the $L_{\rm sph} - n_{\rm sph}$ and $M_{\rm BH} - n_{\rm sph}$ diagrams 
with the same galaxy sample used in \emph{Paper II} (and presented here in Table \ref{tab:sample}), 
i.e.~66 galaxies for which a dynamical measurement of the black hole mass has been reported in the literature 
(by \citealt{grahamscott2013} or \citealt{rusli2013}) 
and for which we were able to successfully model the light distribution and measure the spheroid structural parameters 
using $3.6\rm~\mu m$ \emph{Spitzer} satellite images. 
Our galaxy decompositions take into account bulge, disks, spiral arms, bars, rings, halo, 
extended or unresolved nuclear source and partially depleted core, 
and -- for the first time -- they were checked to be consistent with the galaxy kinematics 
\citep{atlas3dIII,scott2014,arnold2014}. 
Kinematical information was used to confirm the presence of disk components 
in the majority of early-type (elliptical + lenticular) galaxies and, more importantly,  
to estabilish the radial extent of these disks, 
which in most cases is not obvious from a visual inspection of the galaxy images. 
This enabled us to distinguish between intermediate-scale disks, 
that are fully embedded in the spheroid,  
and large-scale disks, that encase the bulge and dominate the light at large radii.  
Savorgnan \& Graham (2015) explain that when an intermediate-scale disk is misclassified and modeled as a large-scale disk, 
the luminosity of the spheroid is underestimated, 
hence the galaxy incorrectly appears as a positive outlier (an ``over-massive'' black hole) in the $M_{\rm BH} - L_{\rm sph}$ diagram. 
A detailed description of the dataset used here, the data reduction process and the galaxy modelling technique that we developed 
can be found in \emph{Paper I}, 
along with a discussion of how we estimated the uncertainties on the spheroid S\'ersic indices\footnote{The uncertainties associated with 
the spheroid S\'ersic indices have been estimated with a method that takes into account systematic errors. 
This method consists in comparing, for each of our galaxies, the measurements of the spheroid S\'ersic index obtained by different studies 
with that obtained by us. 
Systematic errors are typically not considered by popular 2D fitting codes which report only the statistical errors 
associated with their fitted parameters. 
Refer to \emph{Paper I} for a detailed discussion on this. }.  
The morphological classification (E = elliptical; E/S0 = elliptical/lenticular; S0 = lenticular; 
S0/Sp = lenticular/spiral; Sp = spiral; and ``merger'') follows from the galaxy decompositions illustrated in \emph{Paper I}. 
As in \emph{Paper II}, we will refer to early-type galaxies (E+S0) and late-type galaxies (Sp). 
The early-type bin includes the two galaxies classified as E/S0, 
whereas the two galaxies classified as S0/Sp and the two galaxies classified as mergers are included in neither the early- nor the late-type bin.

@@

\section{Analysis and results}
\label{sec:anal}
As in \emph{Paper II}, a linear regression analysis of the $L_{\rm sph} - n_{\rm sph}$ 
(Table \ref{tab:lregLn} and Figure \ref{fig:magn})
and $M_{\rm BH} - n_{\rm sph}$ (Table \ref{tab:lregMn} and Figure \ref{fig:mbhn}) diagrams 
was performed using three different routines: 
the BCES code from \cite{akritasbershady1996}, 
the FITEXY routine \citep{press1992}, as modified by \cite{tremaine2002}, 
and the Bayesian estimator {\tt linmix\_err} \citep{linmixerr}.
All of these three routines take into account the intrinsic scatter, 
but only the FITEXY and the {\tt linmix\_err} codes allow one to quantify it.
We report both symmetrical and nonsymmetrical linear regressions.  
Symmetrical regressions are meant to be compared with theoretical expectations, 
whereas nonsymmetrical forward ($Y|X$) regressions -- which minimize the scatter in the $Y$ direction -- 
allow one to predict the value of the observable $Y$ with the best possible precision. \\
We searched for extreme outliers in both the $L_{\rm sph} - n_{\rm sph}$ and $M_{\rm BH} - n_{\rm sph}$ diagrams, 
and found that in our $L_{\rm sph} - n_{\rm sph}$ plot there are no $3\sigma$ outliers, 
whereas in our $M_{\rm BH} - n_{\rm sph}$ plot 
the S0 galaxies NGC 0524 and NGC 3998 reside more than $3\sigma$ from the bisector linear regression for all galaxies. 
These two galaxies have therefore been excluded from the rest of the analysis. {\bf mergers are excluded?? 62??} \\
{\bf fitexy does better job, we report that} \\

\subsection{$L_{\rm sph} - n_{\rm sph}$}
Following \cite{graham2001}, 
who showed that the $L_{\rm sph} - n_{\rm sph}$ relation is different for elliptical galaxies and the bulges of disk galaxies (S0+Sp), 
\cite{savorgnan2013} re-analyzed the data from \cite{grahamguzman2003} and \cite{graham2013review} 
and obtained two separate $L_{\rm sph} - n_{\rm sph}$ linear regressions for elliptical galaxies and the bulges of disk galaxies 
(in the B- and K-band, respectively). 
At the time, the $L_{\rm sph} - n_{\rm sph}$ datasets from \cite{grahamguzman2003} and \cite{graham2013review} were of the best quality available 
to investigate the $L_{\rm sph} - n_{\rm sph}$ relation for different galaxy morphological types. 
However, these datasets were not obtained from a homogeneous analysis, 
but they were a collection of results taken from various past bulge/disk decomposition studies. 
It is also worth mentioning that, 
although the K-band luminosities of the bulges of disk galaxies had been corrected for internal dust absorption, 
{\bf the dust corrections are not precise today refs??, imagine at the time.....}  
Here we re-investigate the $L_{\rm sph} - n_{\rm sph}$ diagram with our high-quality dataset  
derived from state-of-the-art multicomponent decompositions, 
that were performed in a consistent manner 
and using the $3.6\rm~\mu m$ band, which is less affected by dust extinction than the K-band. \\
\cite{graham2013review} presented a single $L_{\rm sph} - n_{\rm sph}$ correlation for the bulges of disk galaxies (S0+Sp).
However, using our dataset, 
we fit the $L_{\rm sph} - n_{\rm sph}$ relation for elliptical, lenticular and spiral galaxies separately, 
and found that the values of the slope and intercept for the lenticular galaxies 
are not consistent within the errors with those for the spiral galaxies, 
but are consistent within the errors with those for the elliptical galaxies.  
Given this, we conclude that in the $L_{\rm sph} - n_{\rm sph}$ diagram 
elliptical and lenticular galaxies form together a single (\emph{early-type}) sequence, 
whereas the combination of lenticular and spiral galaxies do not. 
{\bf why?? dust? multicomponent? classification?}

\begin{figure}[h]
\begin{center}
\includegraphics[width=\columnwidth]{images/mag_vs_n_maj.pdf}
\caption{Spheroid absolute magnitude (at $3.6\rm~\mu m$) plotted against spheroid S\'ersic index 
measured along the galaxy major-axis. 
Symbols are coded according to the galaxy morphological type (see legend).
The orange crosses denote two lenticular galaxies (NGC 0524 and NGC 3998) which were excluded from the linear regression analysis 
(see Section \ref{sec:anal}). 
The red dashed line indicates the FITEXY bisector linear regression for the $45-2=43$  early-type galaxies (E+S0), 
with the red shaded area denoting its $1\sigma$ uncertainty. 
The shallower blue solid line shows the FITEXY bisector linear regression for the bulges of the 17 late-type (Sp) galaxies, 
with the blue shaded area denoting its $1\sigma$ uncertainty. 
The inset panel shows the error bars associated to each data point,  
where the error bars have the same color coding as the symbols in the main figure. 
}
\label{fig:magn}
\end{center}
\end{figure}

\subsection{$M_{\rm BH} - n_{\rm sph}$}
\cite{grahamscott2013} presented two different $M_{\rm BH} - L_{\rm sph}$ relations for S\'ersic and core-S\'ersic 
spheroids\footnote{Core-S\'ersic spheroids have partially depleted cores relative to their outer S\'ersic light profile, 
whereas S\'ersic spheroids have no central deficit of stars. } \citep{graham2003coresersicmodel,trujillo2004coresersicmodel}.
However, in \emph{Paper II} we found that the slopes of the $M_{\rm BH} - L_{\rm sph}$ correlations for S\'ersic and core-S\'ersic spheroids 
are consistent with each other within their $1\sigma$ uncertainties, 
which prevents us from considering them as two separate sequences. 
On the other hand, our analysis showed that early- and late-type galaxies follow two different $M_{\rm BH} - L_{\rm sph}$ relations 
($M_{\rm BH} \propto L_{\rm sph}^{1.00 \pm 0.10}$ 
and $M_{\rm BH} \propto L_{\rm sph}^{2.88 \pm 0.68}$, respectively). \\
Given that early- and late-type galaxies define two separate sequences in both the $L_{\rm sph} - n_{\rm sph}$ 
and $M_{\rm BH} - L_{\rm sph}$ diagrams, 
we investigate substructure in the $M_{\rm BH} - n_{\rm sph}$ diagram. 
Using the results from the modified FITEXY routine, 
we find that 
early-type galaxies follow $M_{\rm BH} \propto n_{\rm sph}^{3.58 \pm 0.27}$, 
while late-type galaxies follow $M_{\rm BH} \propto n_{\rm sph}^{4.55 \pm 0.66}$. 
The Bayesian estimator {\tt linmix\_err} returns consistent results: 
a slope of $3.44 \pm 0.33$ for the early-type galaxies 
and a slope of $4.12 \pm 1.07$ for the late-type galaxies. 
In both cases, the values of the slope and intercept for the early- and late-type galaxies 
are consistent with each other within their $1\sigma$ uncertainties\footnote{In effect, 
considering the results of the modified FITEXY routine, 
the slopes of the relations for early- and late-type galaxies 
are only marginally consistent with each other within their $1\sigma$ uncertainties. 
However, the same slopes obtained with Bayesian estimator {\tt linmix\_err} 
are fully consistent with each other within their $1\sigma$ uncertainties. }.
Our analysis shows that the early- and late-type galaxies do not follow two separate trends in the $M_{\rm BH} - n_{\rm sph}$ diagram, 
i.e.~we do not identify any significant substructure based on the galaxy morphological type. \\
The symmetrical linear regression for all galaxies obtained with the modified FITEXY routine is: 
\begin{equation}
\log \biggl( \frac{M_{\rm BH}}{\rm M_\odot} \biggr) = (8.18 \pm 0.06) + (3.39 \pm 0.15) \bigl(\log n_{\rm sph}^{\rm maj} - 0.51 \bigr) .
\end{equation}

\begin{figure}[h]
\begin{center}
\includegraphics[width=\columnwidth]{images/mbh_vs_n_maj.pdf}
\caption{Black hole mass plotted against spheroid S\'ersic index measured along the galaxy major-axis. 
Symbols are coded according to the galaxy morphological type (see legend). 
The orange crosses denote two lenticular galaxies (NGC 0524 and NGC 3998) which were excluded from the linear regression analysis 
(see Section \ref{sec:anal}). 
The red dashed line indicates the FITEXY bisector linear regression for the $45-2=43$  early-type galaxies (E+S0), 
with the red shaded area denoting its $1\sigma$ uncertainty. 
The shallower blue solid line shows the FITEXY bisector linear regression for the bulges of the 17 late-type (Sp) galaxies, 
with the blue shaded area denoting its $1\sigma$ uncertainty. 
The linear regressions for early- and late-type galaxies are consistent with each other within their $1\sigma$ uncertainties.  
The inset panel shows the error bars associated to each data point,  
where the error bars have the same color coding as the symbols in the main figure. 
}
\label{fig:mbhn}
\end{center}
\end{figure}

\section{Discussion and conclusions} 
We have seen that the early- and late-type galaxies in the $M_{\rm BH} - n_{\rm sph}$ diagram can be fit with a single power-law, 
whereas they follow two separate correlations in the $M_{\rm BH} - L_{\rm sph}$ diagram (\emph{Paper II}). 
We now want to compare the amount of scatter among these two plots. 
When considering all galaxies, irrespective of their morphological type, 
the intrinsic scatter of the $M_{\rm BH} - n_{\rm sph}$ relation is smaller than that of the $M_{\rm BH} - L_{\rm sph}$ relation. 
However, because of the different nature of the $M_{\rm BH} - n_{\rm sph}$ and $M_{\rm BH} - L_{\rm sph}$ correlations 
(single and double power-law, respectively),  
we are not comparing apples with apples. 
One can obtain more informative results by considering early- and late-type galaxies separately. 
For early-type galaxies only, the intrinsic scatter of the $M_{\rm BH} - n_{\rm sph}$ relation is consistent\footnote{Looking 
at the results obtained with the modified FITEXY routine, 
the values of the intrisic scatter are only marginally consistent with each other, 
but looking at the results obtained with the Bayesian estimator {\tt linmix\_err}, 
the values of the intrisic scatter are fully consistent with each other. } with  
that of the $M_{\rm BH} - L_{\rm sph}$ relation (within their $1\sigma$ uncertainties). 
For late-type galaxies only, the intrinsic scatter of the $M_{\rm BH} - n_{\rm sph}$ relation is consistent with 
that of the $M_{\rm BH} - L_{\rm sph}$ relation, 
{\bf except fitexy xy}.

data suggest that m-n more fundamental than l-n or m-l woooooh? \\

\begin{table*}
\centering
\caption{Linear regression analysis of the $L_{\rm sph} - n_{\rm sph}$ diagram.}
\begin{tabular}{llccccc}
\tableline
\tableline
{\bf Subsample (size)} & {\bf Regression} & $\boldsymbol \alpha$ & $\boldsymbol \beta$ & $\boldsymbol \langle \log n_{\rm sph}^{\rm maj} \rangle$ & $\boldsymbol \epsilon$ & $\boldsymbol \Delta$ \\ 
\tableline 
\\
 & \multicolumn{6}{l}{$MAG_{\rm sph}/{\rm [mag]} = \alpha + \beta \bigl(\log n_{\rm sph}^{\rm maj} - \langle \log n_{\rm sph}^{\rm maj} \rangle \bigr)$} \\ [0.5em]
All (62)               & BCES $(Y|X)$               & $-23.88 \pm 0.15$ & $-7.17 \pm 0.80$ & $0.51$ & $-$ & $1.18$ \\
                       & mFITEXY $(Y|X)$            & $-23.95 \pm 0.13$ & $-6.70 \pm 0.45$ & $0.51$ & $0.56^{+0.15}_{-0.10}$ & $0.98$ \\
                       & {\tt linmix\_err} $(Y|X)$  & $-23.92 \pm 0.15$ & $-6.40 \pm 0.57$ & $0.51$ & $0.74 \pm 0.13$ & $1.07$ \\ [0.5em]
                       & BCES $(X|Y)$               & $-23.88 \pm 0.14$ & $-6.70 \pm 0.51$ & $0.51$ & $-$ & $1.11$ \\
                       & mFITEXY $(X|Y)$            & $-23.94 \pm 0.14$ & $-7.50 \pm 0.52$ & $0.51$ & $0.59^{+0.17}_{-0.11}$ & $1.23$ \\
                       & {\tt linmix\_err} $(X|Y)$  & $-23.94 \pm 0.16$ & $-7.51 \pm 0.62$ & $0.51$ & $0.81 \pm 0.16$ & $1.23$ \\ [0.5em]
                       & BCES Bisector              & $-23.88 \pm 0.14$ & $-6.93 \pm 0.60$ & $0.51$ & $-$ & $1.14$ \\
                       & mFITEXY Bisector           & $-23.94 \pm 0.13$ & $-7.08 \pm 0.34$ & $0.51$ & $-$ & $1.16$ \\
                       & {\tt linmix\_err} Bisector & $-23.93 \pm 0.16$ & $-6.91 \pm 0.42$ & $0.51$ & $-$ & $1.14$ \\ [0.5em]

@@

\begin{table*}
\centering
\caption{Linear regression analysis of the $L_{\rm sph} - n_{\rm sph}$ diagram.}
\begin{tabular}{llccccc}
\tableline
\tableline
{\bf Subsample (size)} & {\bf Regression} & $\boldsymbol \alpha$ & $\boldsymbol \beta$ & $\boldsymbol \langle \log n_{\rm sph}^{\rm maj} \rangle$ & $\boldsymbol \epsilon$ & $\boldsymbol \Delta$ \\ 
\tableline 
\\
Early-type (E+S0) (43) & BCES $(Y|X)$		    & $-24.55 \pm 0.22$ & $-11.84 \pm 2.29$ & $0.64$ & $-$ & $1.50$ \\
		       & mFITEXY $(Y|X)$	    & $-24.74 \pm 0.14$ & $-8.86 \pm 0.66$ & $0.51$ & $0.27^{+0.20}_{-0.27}$ & $0.87$ \\
		       & {\tt linmix\_err} $(Y|X)$  & $-24.70 \pm 0.17$ & $-8.28 \pm 0.87$ & $0.64$ & $0.58 \pm 0.17$ & $0.98$ \\ [0.5em]
		       & BCES $(X|Y)$		    & $-24.55 \pm 0.14$ & $-8.25 \pm 0.63$ & $0.64$ & $-$ & $0.96$ \\
		       & mFITEXY $(X|Y)$	    & $-24.74 \pm 0.14$ & $-9.13 \pm 0.68$ & $0.64$ & $0.23^{+0.25}_{-0.23}$ & $1.08$ \\
		       & {\tt linmix\_err} $(X|Y)$  & $-24.73 \pm 0.18$ & $-9.08 \pm 0.87$ & $0.64$ & $0.60 \pm 0.21$ & $1.07$ \\ [0.5em]
		       & BCES Bisector  	    & $-24.55 \pm 0.17$ & $-9.73 \pm 1.05$ & $0.64$ & $-$ & $1.14$ \\
		       & mFITEXY Bisector	    & $-24.74 \pm 0.14$ & $-8.99 \pm 0.48$ & $0.64$ & $-$ & $1.06$ \\
		       & {\tt linmix\_err} Bisector & $-24.72 \pm 0.17$ & $-8.66 \pm 0.63$ & $0.64$ & $-$ & $1.02$ \\ [0.5em]

@@

  \begin{table*}
  \centering
  \caption{Intrinsic scatter of the $M_{\rm BH} - n_{\rm sph}$ and $M_{\rm BH} - L_{\rm sph}$ relations.}
  \begin{tabular}{llccr}
  \tableline
  \tableline
  {\bf Subsample} & {\bf Regression} & $\boldsymbol \epsilon$ {\bf for} $\boldsymbol M_{\rm BH} - n_{\rm sph}$ & 
  $\boldsymbol \epsilon$ {\bf for} $\boldsymbol M_{\rm BH} - L_{\rm sph}$ & \\ 
  \tableline 
  \\
  All		  & mFITEXY $(Y|X)$	      & $0.22^{+0.10}_{-0.07}$ & $0.49^{+0.06}_{-0.05}$ & non consist. \\
 		  & {\tt linmix\_err} $(Y|X)$ & $0.29 \pm 0.07$ & $0.51 \pm 0.06$               & non consist. \\
 		  & mFITEXY $(X|Y)$	      & $0.23^{+0.10}_{-0.07}$ & $0.58^{+0.07}_{-0.06}$ & non consist. \\
 		  & {\tt linmix\_err} $(X|Y)$ & $0.30 \pm 0.07$ & $0.60 \pm 0.09$               & non consist. \\ [0.5em]

  Early-type	  & mFITEXY $(Y|X)$	      & $0.24^{+0.10}_{-0.07}$ & $0.40^{+0.06}_{-0.05}$ & marg. consist. \\
 		  & {\tt linmix\_err} $(Y|X)$ & $0.32 \pm 0.08$ & $0.41 \pm 0.06$               & consist. \\
 		  & mFITEXY $(X|Y)$	      & $0.26^{+0.11}_{-0.08}$ & $0.49^{+0.08}_{-0.06}$ & marg. consist. \\
 		  & {\tt linmix\_err} $(X|Y)$ & $0.35 \pm 0.10$ & $0.51 \pm 0.10$               & consist. \\ [0.5em]
